---
  title: "Data analyse"
author: "Adam finnemann & Line"
date: "November 20, 2017"
---
  
  
  

```{r}
library(tidyverse)
library(lmerTest)
setwd("~/cogsci/Mind and consciousness/exam/python")
da <- read.delim("preprocessed_data.csv", sep = ",")

da %>% 
  filter(!duplicated(ID)) %>% 
  group_by(gender) %>% 
  tally()

da %>% 
  filter(!duplicated(ID)) %>% 
  group_by(Nationality) %>% 
  tally()


#Assuming we did two experiment

contrast_exp = da %>% 
  filter(type =="contrast")

person_exp = da %>% 
  filter(type =="person")

```


##Analysis of contrast experiment

Removing people without knowledge of newspapers
```{r}
contrast_exp <- contrast_exp  %>% 
  filter(competence != 0) %>% 
  mutate(condition = as.factor(condition),
         condition = dplyr::recode(condition, "0" = "threat_second", "1" = "threat_first"))




```


Analysing reading times

```{r}
contrast_exp  %>%
  group_by(condition) %>% 
  summarise(mean = mean(rt_text),
            sd = sd(rt_text))



```
We see no major difference between first and second article

```{r}
contrast_exp  %>%
  summarise(mean = mean(rt_text),
            sd = sd(rt_text))

```


#analysing outliers
```{r}
contrast_exp %>%  filter(rt_text < 10)

contrast_exp = contrast_exp %>%
  filter(rt_text > 10) 
```

Demographic descriptors
```{r}
contrast_exp %>% 
  filter(!duplicated(ID)) %>% 
  group_by(gender) %>% 
  tally()
```
24 F and 9 M left after preprocessing. 6 excluded

```{r}
contrast_exp %>% 
  filter(!duplicated(ID)) %>% 
  group_by(Nationality) %>% 
  tally()

```




```{r}
contrast_exp$ID = as.factor(contrast_exp$ID)
mdl2 = lmer(competence ~ threat*condition +(threat|ID) + (threat|topic),contrast_exp)
summary(mdl2)
```








```{r}
leveneTest(residuals(mdl2) ~ as.factor(contrast_exp$ID))
```
```{r}
leveneTest(residuals(mdl2) ~ as.factor(contrast_exp$topic))
```

```{r}
leveneTest(residuals(mdl2) ~ as.factor(contrast_exp$threat))

```
```{r}
leveneTest(residuals(mdl2) ~ as.factor(contrast_exp$condition))

```

##Power analysis

```{r}
library(pacman)
p_load(tidyverse, stringr, simr, lmerTest, simr)

test_mdl = lmer(competence ~ threat + condition +(threat|ID) ,contrast_exp)

powersim_threat = powerSim(test_mdl, fixed("threat"), nsim=200)

powersim_threat
```

```{r}
powersim_threat = powerSim(test_mdl, fixed("condition"), nsim=200)

powersim_threat

```
```{r}
test_mdl = lmer(competence ~ threat*condition +(threat|ID) ,contrast_exp)

powersim_threat = powerSim(test_mdl, fixed("threat:condition"), nsim=200)

powersim_threat
```


###Analysis of person stories
Removing people without knowledge of newspapers


```{r}
person_exp <- person_exp  %>% 
  filter(competence != 0)

```


analysing outliers
```{r}
person_exp %>%  filter(rt_text < 10)




person_exp = person_exp %>%
  filter(rt_text > 10) 
```

```{r}
person_exp %>% 
  group_by(threat) %>% 
  tally()

person_exp %>% 
  group_by(topic, threat) %>% 
  tally()
```


```{r}
mdl3 = lmer(competence ~ threat + (threat|ID) + (threat|topic), person_exp)

summary(mdl3)



```

Checking for assumptions:
Homoskedasticity (homogenity of variance) using levene's test
```{r}

leveneTest(residuals(mdl3) ~ as.factor(person_exp$ID))
```
```{r}
leveneTest(residuals(mdl3) ~ as.factor(person_exp$topic))
```

```{r}
leveneTest(residuals(mdl3) ~ as.factor(person_exp$threat))
```



Assumption of normality
```{r}
library(lattice)
qqmath(mdl3)

library(pastecs)

stat.desc(resid(mdl3), norm = T, basic = F)

shapiro.test(resid(mdl3))

stat.desc(resid(mdl3), norm = T)

hist(resid(mdl3))
shapiro.test(resid(mdl3))

```



```{r}
ggplot(person_exp, aes(threat, competence)) +
  geom_bar(stat = "summary", fun.y = "mean", aes(fill = threat)) +
  geom_errorbar(stat = "summary", fun.data = "mean_se", width = 0.1)

```




```{r}
library(sjPlot)
sjp.lmer(mdl3, type = "fe.cor")
```


```{r}
glmer_mdl <- glmer(threat ~ news_paper + (1|ID), da, family = "binomial")

inv.logit(glmer_mdl@beta)
summary(glmer_mdl)
```

```{r}

glmer_mdl

predict(glmer_mdl)


da <- da %>% 
      mutate(predictions_perc = inv.logit(predict(glmer_mdl)),
             predictions = ifelse(predictions_perc > 0.5, "threat","safe"),
             predictions = as.factor(predictions))
    
library(caret)
    conf_mat <- caret::confusionMatrix(data = da$predictions, reference = da$threat, positive = "threat") 
caret::confusionMatrix(data = da$predictions, reference = da$threat, positive = "threat") 

library(boot)
minv.logit(glmer_mdl@beta)


  #creating folds  
  Subjects = unique(da$Subject)
  folds <- createFolds(Subjects, 5)
  
  #running loop
  cross_val <- sapply(seq_along(folds), function(x) {
    
    train_folds = filter(da, !(as.numeric(Subject) %in% folds[[x]]))
    predict_fold = filter(da, as.numeric(Subject) %in% folds[[x]])
    
    train_model <-  glmer(model_formula, train_folds ,family="binomial")
    
    
    predict_fold <- predict_fold %>% 
      mutate(predictions_perc = inv.logit(predict(train_model, predict_fold, allow.new.levels = T)),
             predictions = ifelse(predictions_perc > 0.5, "Schizophrenia","Control"),
             predictions = as.factor(predictions))
    
    conf_mat <- caret::confusionMatrix(data = predict_fold$predictions, reference = predict_fold$Diagnosis, positive = "Schizophrenia") 
    
    accuracy <- conf_mat$overall[1]
    sensitivity <- conf_mat$byClass[1]
    specificity <- conf_mat$byClass[2]
    
    predict_fold$Diagnosis <- as.factor(predict_fold$Diagnosis)
    rocCurve <- roc(response = predict_fold$Diagnosis,   predictor = inv.logit(test))
    
    auc(rocCurve) 
    
    
    fixed_ef <- fixef(train_model) 
    
    output <- c(accuracy, sensitivity, specificity, fixed_ef)
    


```

